Generalized Linear Mixed Models

### 2009-04-02 docs/inla/inla.rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@171 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{frame}
\frametitle{Markov Chain Monte Carlo}
\begin{itemize}
	\item Put prior distributions on parameters $[\sigma]$, $[\beta]$.
	\item Simulate from the posterior distributions
	\[
	[\sigma|Y],\ [\beta|Y],\ [V|Y]
	\]
	\item 
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Example:}

@@

\begin{frame}
\frametitle{Example: Lung cancer in Ontario}
<<cancerInla>>=
library(diseasemapping)
library(sp)
data(popdata)
data(casedata)
model = getRates(casedata, popdata, ~age*sex)
ontario = getSMR(popdata,model,  casedata)
data(popDataAdjMat)

# fit bym model 
#forBugs = glmmBUGS(formula=Observed + logExpected ~ 1,
#  effects="CSDUID",   family="poisson", spatial=popDataAdjMat,
#  data=ontario)

>>>>

\begin{frame}
\frametitle{Markov Chain Monte Carlo}
\begin{itemize}
	\item Put prior distributions on parameters $[\sigma]$, $[\beta]$.
	\item Simulate from the posterior distributions
	\[
	[\sigma|Y],\ [\beta|Y],\ [V|Y]
	\]
	\item Use $[V|Y] = [Y|V][V]/[Y]$, but $[Y]$ is impossible to evaluate.
	\item Gibbs sampler: alternate between sampling from $[V|Y,\beta,\sigma]$ and $[\beta,\sigma|V,Y]$.
	\item Random walk Metropolis: update $V_i^{(p)}$ to  $V_i^{(p+1)}~N(V_i^{(p)}, \nu^2)$, accept the move with probability
	\[
	\min[1, pr(Y|V_i^{(p+1)}) /  pr(Y|V_i^{(p)})) ]
	\]
	\item This is guaranteed to converge to a sample from $[V_i|Y]$\ldots
	\item \ldots eventually
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Example:bacteria}
<<bacmcmc,fig=false,echo=true>>=
library(glmmBUGS)
bac = glmmBUGS(y ~ trt, effects='ID', family='binomial',data=bacteria, file='modelx.bug')
startingValues = bac$startingValues
source("getInits.R")
library(BRugs)
library(R2WinBUGS)
bacResult = bugs(bac$ragged, getInits, 
	parameters.to.save = names(getInits()),
  model.file="model.bug", n.chain=3, n.iter=1000, n.burnin=100, n.thin=10,
                             program="openbugs") 
bacParams = restoreParams(bacResult, bac$ragged)

@@

\begin{frame}
\frametitle{Example: Lung cancer in Ontario}
<<cancerInla>>=
if(F) {
library(diseasemapping)
library(sp)
data(popdata)
data(casedata)
model = getRates(casedata, popdata, ~age*sex)
ontario = getSMR(popdata,model,  casedata)
data(popDataAdjMat)

# fit bym model with inla, like
#forBugs = glmmBUGS(formula=Observed + logExpected ~ 1,
#  effects="CSDUID",   family="poisson", spatial=popDataAdjMat,
#  data=ontario)
}
@
\end{frame}
